On Sample Size for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-19 Manuscript/manuscript.tex
Update

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, let
$\hat{\theta}_{(i)}$ be the jackknife values of $Z_{(i)}$
for $i \in \{1, \ldots, n\}$, 
and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}
.\] For a $(1 - \alpha)100\%$ CI, let
\[
\alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}\right).
\]
\[
\alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}\right).
\]
A $(1 - \alpha)100\%~BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the 
rate of change of of the standard error of $\hat\theta_n$ with respect to
$\theta$.

@@

Based on Figure~\ref{fig:mu}, 
Student's $t$ CIs appear to have the highest \eds{largest?} \mc{addressed} coverage rates with 
respect 
to estimating $\mu$. In fact, for $\phi = -0.4$, Student's $t$ CIs over-cover 
$\mu$ for all sample sizes, whereas other CIs have coverage rates that
hover around the $95\%$ line at this level of $\phi$. For $\phi \geq -0.2$,
$BC_a$ CIs undercover $\mu$ for all $n$ observed. For $\phi = -0.2$, 
Standard, Percentile, %CBP, 
Proposed Method, and $BC$ CIs seem to 
generally cover $\mu$ at the nominal 
rate when $n \geq 400$. Student's $t$ CIs either recover or over-cover $\mu$
for $n \geq 100$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n = 1600$ seems to 
be enough to recover $\mu$ when using Standard, Percentile, 
%CBP, 
Proposed Method, or $BC$ 
CIs. Student's $t$ CIs cover $\mu$ at the nominal rate for $n \geq 100$ at 
$\phi = 0$.
For $\phi = 0.2$, $n > 3200$ seems to be necessary to recover $\mu$
at the nominal level when using
any of the CIs, although some CIs, such as Student's $t$, are much closer to the
$95\%$ line than others, most notably $BC_a$.
For $\phi = 0.4$, a much larger sample size appears to be necessary. Once again,
Student's $t$ CIs are the closest to $95\%$ coverage, and $BC_a$ CIs are the 
furthest.

Based on Figure~\ref{fig:sigma}, 
$BC_a$ CIs greatly undercover $\sigma_x$ for every combination of $n$ and 
$\phi$ observed, although there is no trend of coverage deterioration, 
indicating that there may eventually
be a sample size large enough for $\sigma_x$ to be covered at the nominal level.
For $\phi = -0.4$, Standard Normal and Student's $t$ CIs recover $\sigma_x$ when 
$n = 1600$, but undercover $\sigma_x$ for $n = 3200$, indicating
that a larger $n$ is most likely necessary to consistently cover $\sigma_x$ at 
the nominal rate.
The other CI types undercover $\sigma_x$ for all sample sizes at $\phi = 0.4$.
For $\phi  = -0.2$, all CIs except for $BC_a$ are able to cover $\sigma_x$ at 
the nominal rate for $n \geq 3200$, and Student's $t$ CIs cover $\sigma$ at the 
nominal rate when $n \geq 400$. When $\phi = 0$, $n \geq 1600$ seems to 
be large enough if Standard CIs are used, and $n \geq 400$ is fine is
Student's $t$ CIs are used. $n \geq 3200$ appears necessary 
for other CIs. For $\phi = 0.2$, 
comfortable coverage of $\sigma_x$ at the nominal level appears to only be true
for Student's $t$ CIs for $n \geq 3200$, although Standard %and CBP% 
CIs do reach the nominal level in our simulation results. For $\phi = 0.4$, a much
larger sample size appears to be necessary. Student's $t$ CIs are the closest to
$95\%$ coverage, and $BC_a$ CIs are the furthest.

Based on Figure~\ref{fig:phi}, 
Percentile, %CBP, %
$BC$, and $BC_a$ CIs deteriorate clearly for any level of temporal correlation,
so they should not be used. The deterioration becomes more evident
as the absolute value of $\phi$ increases, regardless of whether $\phi$ is 
negative or positive. When $\phi = -0.4$, Standard and Proposed Method CIs 
recover $\phi$ at the nominal rate for $n \geq 400$. At this $\phi$ level,
Student's $t$ CIs either recover or over-cover $\phi$ for $n \geq 100$. When
$\phi = -0.2$, Standard and Proposed Method CIs recover $\phi$ at $n = 800$ and 
$n = 1600$, 
although they undercover $\phi$ at $n = 3200$, indicating that 
perhaps a larger $n$ is needed if these CIs are used. However,
Student's $t$ CIs cover $\phi$ at the nominal level for $n \geq 400$. When
$\phi = 0$, Standard and Proposed Method CIs recover $\phi$ relatively 
comfortably at $n = 3200$, and 
$n = 800$ seems to be sufficient for Student's $t$ CIs. For $\phi = 0.2$, Standard
and Proposed Method CIs cover $\phi$ at the nominal rate for $n \geq 1600$, whereas 
Student's $t$ CIs can accomplish this at $n \geq 100$. For $\phi = 0.4$, $n \geq 
800$ is large enough for Standard and Proposed Method CIs. Student's $t$ CIs either
recover or over-cover $\phi$ for all $n \geq 100$.

To summarize, the CI type chosen should be based on the target parameter. 
When estimating $\mu$, the Student's $t$ CI seems to have the highest coverage
overall, although that leads to over-coverage when $\phi$ is -0.4. For a
sample with no temporal dependence, the Student's $t$ CI cover $\mu$ perfectly
at the nominal rate even for small sample sizes. For positive $\phi$, a larger
sample size appears to be necessary regardless of the CI used. In the case
that $\phi$ is unknown and expected to be greater than $0$, $n > 3200$ may be
necessary for block bootstrap interval estimation of $\mu$. If $\phi$ is known,
a lesser sample size may be sufficient. When estimating $\sigma_x$,
$BC_a$ should not be used, and Student's $t$ again has the highest
\eds{highest?} \mc{addressed} coverage
rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
$n > 3200$ may be necessary for block bootstrap interval estimation of
$\sigma_x$. Again, if $\phi$ is known, a lesser sample size may be enough.
When estimating $\phi$, Percentile and $BC_a$ CIs 
deteriorate in coverage, indicating they should not be used in this context. 
Increasing $n$ will not fix the performance of either of these intervals 
because the assumption that the coverage rate will approach the nominal level
as $n$ increases is invalid. Standard and Proposed Method CIs managed to fix the
deterioration problem, and they perform similarly, but Student's $t$ covers
$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
$n = 800$ is large enough to
recover $\phi$ when using the Student's $t$ method.

@@

When using Student's $t$ intervals and $\phi$ is
unknown, the results of this study suggest that an $n > 3200$ may be
necessary for common practice to estimate simpler parameters like $\mu$ 
or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
to
estimate these parameters. For lower absolute values of $\phi$, a smaller
$n$ is sufficient when estimating $\mu$ or $\sigma$. For negative
values of $\phi$, coverage of $\mu$ is higher in general. In fact, 
Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$, 
meaning that if $\phi$ is known to have a very negative value, another CI
should be used.
However, in real world applications, $\phi$ is
more commonly found to be positive, so Student's $t$ should still be used
if $\phi$ is unknown.
Lastly, to estimate $\phi$, an $n$ of around $800$ using the 
Student's $t$ method
 may be sufficient.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.

>>>>

\paragraph{Bias Corrected and Accelerated ($BC_a$) Bootstrap CI}
The $BC_a$ CI was first suggested in \citet{efron1987better}.
\jy{Isn't this just the empirical CDF? We just need the sample quantile functon.
  What is your reference for this description?}
Let $\hat{z}_0 = \Phi^{-1}\{\#\{\hat\theta_n^{(b)} < \hat{\theta}_n\} / B\}$
for $b \in \{1, \ldots, B\}$. 
Let $Z_{(i)}$ be the original sample without the $i$th block $z_i$, let
$\hat{\theta}_{(i)}$ be the jackknife values of $Z_{(i)}$
for $i \in \{1, \ldots, n\}$, 
and let $\hat{\theta}_{(.)} = \sum_{i=1}^{k} \hat{\theta}_{(i)} / k$. 
Let 
\[
\hat{a} = \frac{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^3}{6\{\sum_{i=1}^{k} (\hat{\theta}_{(.)} -
  \hat{\theta}_{(i)})^2\}^{3/2}}
.\] For a $(1 - \alpha)100\%$ CI, let
\[
\alpha_1 = \Phi\left(z_0 + \frac{z_{0} +
  z_{\alpha/2}}{1 - \hat{a}(z_{0} + z_{\alpha/2})}\right).
\]
\[
\alpha_2 = \Phi\left(z_0 + \frac{z_{0} +
  z_{1 - \alpha/2}}{1 - \hat{a}(z_{0} + z_{1 - \alpha/2})}\right).
\]
A $(1 - \alpha)100\%~BC_a$ CI is
\[
(\hat\theta_{n, \alpha_1}^{(b)}, \quad \hat\theta_{n, \alpha_2}^{(b)}).
\]
This CI is not necessarily centered by the point estimator $\hat\theta_n$. The
$BC_a$ method corrects for bias and skewness of the $B$ bootstrap point
estimates $\{\hat\theta_n^{(1)}, \ldots, \hat\theta_n^{(B)}\}$ by including
bias-correction and acceleration factors. The acceleration factor refers to
the 
rate of change of the standard error of $\hat\theta_n$ with respect to
$\theta$.

@@

Based on Figure~\ref{fig:mu}, Student's $t$ seems to generally
be the best method for estimating $\mu$.
For $\phi = -0.4$, Student's $t$ CIs over-cover 
$\mu$ for smaller $n$, whereas other CIs recover $\mu$ at the
nominal rate for all $n$ observed. For 
$\phi = -0.2$, 
all CIs recover $\mu$ at the nominal rate for all $n$. For $\phi = 0$, or when the 
sample is independently normally distributed, $n \geq 200$ seems to 
be large enough to recover $\mu$ at the nominal rate when using any CIs
 besides Student's $t$ CIs, which seem to recover $\mu$ at the nominal rate for
  all $n$.
For $\phi = 0.2$, $n \geq 800$ seems to be sufficient to recover $\mu$
at the nominal level when using
any CIs besides Student's $t$ CIS, which recover $\mu$ at the nominal
 rate for all $n \geq 200$.
For $\phi = 0.4$, $n \geq 3200$ seems to be large enough to recover $\mu$
at the nominal level when using
any CIs besides Student's $t$ CIS, which seem to recover $\mu$ at the nominal
 rate for all $n \geq 800$.

Based on Figure~\ref{fig:sigma}, Student's $t$ also seems to generally
be the best method for estimating $\sigma$.
for $\phi = -0.4$, $n \geq 1600$ is sufficient to recover $\sigma$
at the nominal level when using
any CIs besides Standard CIs, which seem to recover $\sigma$ at the nominal 
rate for all $n \geq 800$, and Student's $t$ CIs, which seem to recover $\sigma$
at the nominal rate for all $n \geq 400$. For $\phi = -0.2$, $n \geq 200$ is 
adequate to recover $\sigma$ at the nominal rate with Student $t$ CIs, 
but other CIs seem to require $n \geq 800$. For $\phi = 0$, or when the sample
is independently normally distributed, $n \geq 400$ seems to be about enough
to recover $\sigma$ for all CIs, but Student's $t$ CIs can recover $\sigma$ for
$n \geq 100$. For $\phi = 0.2$, $n \geq 800$ is adequate for CIs besides the
Student's $t$ CI, which recovers $\sigma$ well for $n \geq 200$. For 
$\phi  = 0.4$, $n \geq 1600$ seems necessary for CIs other that Student's $t$ 
CIs, which recover $\sigma$ at the nominal level for $n \geq 400$.

Based on Figure~\ref{fig:phi}, Student's $t$ again seems to generally
be the best method for estimating $\phi$. For high absolute values of $\phi$, 
Percentile, $BC$, and $BC_a$ CIs
deteriorate in coverage as $n$ increases. For $\phi = -0.4$, Standard, Student's
$t$, and Proposed CIs recover $\phi$ for $n \geq 100$. For $\phi = -0.2$, 
Standard and Proposed CIs recover $\phi$ at the nominal rate for $n \geq 200$, 
whereas this can be done for $n \geq 100$ with Student's $t$ CIs. For $\phi = 
0$, or when the sample
is independently normally distributed, Standard and Proposed CIs recover 
$\phi$ at the nominal level  for $n \geq 400$, and this is achievable for 
$n \geq 100$ with Student's $t$ CIs. For $\phi = 0.2$ and $\phi = 0.4$, Standard 
and Proposed CIs recover $\phi$ for $n \geq 200$, and Student's $t$ CIs 
recover $\phi$ for all $n \geq 100$.

To summarize, the CI type chosen should be based on the target parameter. 
When estimating $\mu$, the Student's $t$ CI seems to have the highest
 coverage
overall, although that leads to over-coverage for small sample sizes when $\phi$
 is -0.4. For a
sample with no temporal dependence, the Student's $t$ CI recover $\mu$ 
very close to the nominal rate even for small sample sizes. For positive $\phi$, a
larger sample size appears to be necessary regardless of the CI used. In the
case that $\phi$ is unknown and expected to be greater than $0$, $n > 800$
may be
necessary for block bootstrap interval estimation of $\mu$ when using the Student's $t$ CI. If $\phi$ is known,
a lesser sample size may be sufficient. When estimating $\sigma_x$,
Student's $t$ again has the highest coverage
rates. In the case that $\phi$ is unknown and expected to be greater than $0$,
$n > 400$ may be necessary for block bootstrap interval estimation of
$\sigma_x$ when using the Student's $t$ CI. Again, if $\phi$ is known, a lesser sample size may be enough.
When estimating $\phi$, Percentile, $BC$, and $BC_a$ CIs 
deteriorate in coverage, indicating they should not be used in this context. 
Increasing $n$ will not fix the performance of either of these intervals 
because the assumption that the coverage rate will approach the nominal level
as $n$ increases is invalid. Standard and Proposed Method CIs managed to fix the
deterioration problem, and they perform similarly, but Student's $t$ covers
$\phi$ at the nominal rate for much smaller sample sizes. It seems that 
$n = 100$ is certainly large enough to
recover $\phi$ when using the Student's $t$ method.

@@

When using Student's $t$ intervals and $\phi$ is
unknown, the results of this study suggest that an $n \geq 800$ may be
necessary for common practice to estimate simpler parameters like $\mu$ 
or $\sigma_x$. If $\phi$ is already known, a lesser $n$ may be adequate
to
estimate these parameters. For lower absolute values of $\phi$, a smaller
$n$ is sufficient when estimating $\mu$ or $\sigma$. For negative
values of $\phi$, coverage of $\mu$ is higher in general. In fact, 
Student's $t$ seems to over-cover $\mu$ for $\phi = 0.4$ when using smaller
sample sizes, 
meaning that if $\phi$ is known to have a very negative value, another CI
may be required.
However, in real world applications, $\phi$ is
more commonly found to be positive, so Student's $t$ should still be used
if $\phi$ is unknown.
Lastly, to estimate $\phi$, $n \geq 100$ using the 
Student's $t$ method
 may be sufficient.
Further investigation may be necessary to see if there are other interval
corrections that fix the coverage deterioration problem for $\phi$.
